\documentclass[a4paper,11pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage[top=2.5cm,bottom=2.5cm,outer=2.5cm,inner=2.0cm]{geometry}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage{colortbl}
\usepackage{color,soul}
\usepackage{xcolor}

\usepackage{enumitem}
% \setlist[enumerate,1]{label=\color{blue}(\arabic*)}
\setlist[enumerate,1]{label=(\arabic*)}

\usepackage{graphicx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{hyperref}
\hypersetup{
	colorlinks = true,
	linkbordercolor = {white},
}

\usepackage{listings}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.3}

\usepackage{siunitx}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{subcaption}


\begin{document}

\begin{center}
	{\large\textbf{Imaging Neuroscience \#203: Responses to Editors and Reviewers}}
\end{center}

% Robin: cortex / brain stem / hippocampus /

% ========================================
%     Editor
% ========================================
\noindent \underline{\textbf{Editor}}

\noindent \textit{Dear Zhengguo Tan,\\
\newline
Thanks again for your submission. We would like to give you the opportunity to revise your paper.\\
\newline
This is a very minor revision request with only a couple of minor details remaining.\\
\newline
You can access reviews and submit your revision here: \url{http://janeway.imaging-neuroscience.org/review/article/203/revisions/161/}\\
\newline
Your revisions are due on Jan. 19, 2024.\\
\newline
Regards,\\
Bruce Pike\\
\newline
Imaging Neuroscience}

\vspace{2em}

% ========================================
%     Reviewer 1071
% ========================================
\noindent \underline{\textbf{Reviewer \#1116}}

\noindent \textit{Authors have addressed most of my previous comments. Only exception could be the following:}

\hspace{1em} \textcolor{blue}{Thank you for your constructive reviews in all rounds.}

\begin{enumerate}
    \item [9)] \textit{A few pending points yet to be considered:}

    \item [9a)] \textit{L308: "We tested values of 0, 0.08, and 0.16", these should be changed by new values.}

    \hspace{1em} \textcolor{blue}{Thank you. We corrected these values.}

    \item [9b)] \textit{L319: "Here, the block width of 3 shows the best denoising as compared to 6 and 9, especially in the peripheral brain region" $\rightarrow$ but in Figure 6 you enhance block width of 6 as best case? Importantly, visually unclear which one is providing best denoising results now, so this may need a different reasoning or illustrative example.}

    \hspace{1em} \textcolor{blue}{Thank you. We removed this sentence and
    added another illustrative example in Supporting Information
    to support the use of 6 as the block width.}

\end{enumerate}

\end{document}