\documentclass[a4paper,11pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage[top=2.5cm,bottom=2.5cm,outer=2.5cm,inner=2.0cm]{geometry}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage{colortbl}
\usepackage{color,soul}
\usepackage{xcolor}

\usepackage{enumitem}
% \setlist[enumerate,1]{label=\color{blue}(\arabic*)}
\setlist[enumerate,1]{label=(\arabic*)}

\usepackage{graphicx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{hyperref}
\hypersetup{
	colorlinks = true,
	linkbordercolor = {white},
}

\usepackage{listings}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.3}

\usepackage{siunitx}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{subcaption}


\begin{document}

\begin{center}
	{\large\textbf{Imaging Neuroscience \#203: Responses to Editors and Reviewers}}
\end{center}

% Robin: cortex / brain stem / hippocampus /

% ========================================
%     Editor
% ========================================
\noindent \underline{\textbf{Editor}}

\noindent \textit{Dear Zhengguo Tan,\\
\newline
Thanks again for your submission. We would like to give you the opportunity to revise your paper.\\
\newline
The reviews are largely satisfied with this revision but have a few very minor points that you might consider.\\
\newline
You can access reviews and submit your revision here: \url{http://janeway.imaging-neuroscience.org/review/article/203/revisions/152/}\\
\newline
Your revisions are due on Jan. 12, 2024.\\
\newline
Regards,\\
Bruce Pike\\
\newline
Imaging Neuroscience}

{\color{blue} Thank you for the opportunity
to provide another revision.
We believe that this revision has further improved the quality
of the manuscript and hope that it is ready for publication now.}

\vspace{2em}

% ========================================
%     Reviewer 1071
% ========================================
\noindent \underline{\textbf{Reviewer \#1071}}

\textit{Authors have addressed many of my previous comments but a few pending issues persist:}

\begin{enumerate}
    \item [3.b.1)] \textit{Thanks for the experiment. Think I had a different implementation of MUSE reconstruction in mind when I suggested this experiment. I understand that effect would be negligible for low resolution reconstructions. I appreciate the effort but newly added result may distract from message of paper and does not add much. Therefore, I'd remove it.}

    \hspace{1em} {\color{blue} Thank you for the suggestion.
    We feel this additional experiment that you suggested
    in a previous revision round adds value to the manuscript
    and we chose to keep it.}

    \item [3.b.2)] \textit{I don't think that current discussion is focusing on synergies rather than on similarities. This might be fine, but I suggest to rephrase to provide opinion on whether these methods could complement each other or not.}

    \hspace{1em} {\color{blue} Thank you for the specific suggestion. We rewrote this paragraph. Please refer to the highlighted manuscript with the note R1071.3.b.2.}

    \item [4.a)] \textit{Caption Fig. 6b: "varying block width, keeping lambda 0.08 and stride 1" $\rightarrow$ "varying block width, keeping lambda as 0.08 and stride as 1"}

    \hspace{1em} {\color{blue} Done.}

    \item [7)] \textit{L336: "Figs. 6 and 7 select" $\rightarrow$ "Figs. 6 and 7 show"\\
    L338: "the lower brain region which identifies the" $\rightarrow$ "an inferior brain region with marked"\\
    L339: "the middle" $\rightarrow$ "a middle"
    L440: "the upper brain" $\rightarrow$ "a superior brain"}

    \hspace{1em} {\color{blue} Done.}

    \item [9)] \textit{Thanks for testing the normalization. Seems it is an appropriate prevention for differentiating lambda levels and block size effects. In my opinion authors should replace current Fig. 6 with normalized counterpart, identify new optimal set of parameters, incorporate normalization to manuscript methods, and rerun paper experiments with new optimal configuration.}

    \hspace{1em} {\color{blue} Thank you for the suggestion.
    We included the normalization strategy in the manuscript.}

    \item [12)] \textit{L270-271: "and even partially removes phase variation" $\rightarrow$ "and partially removes phase variation"}

    \hspace{1em} {\color{blue} Done.}

\end{enumerate}

\end{document}